### 2016-11-17 report/survey.tex
Got a table automatically generated by LaTeX. Only put one row in it.

\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in, headheight=15pt]{geometry}
\usepackage{amsmath, amsthm, amsfonts}
\usepackage{hyperref}

@@

\usepackage{titlesec}
\titleformat*{\section}{\large\bfseries}

@@

The

>>>>

\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in, headheight=15pt]{geometry}
\usepackage{amsmath, amsthm, amsfonts}
\usepackage{hyperref}
\usepackage{pgfplotstable}
\pgfplotsset{compat=1.12}
\usepackage{booktabs}
\usepackage{footnote}

@@

@@

\section{Graph Processing Taxonomy}
This is in the spirit of \cite{Doekemeijer:2015:GPFSurvey}.
\begin{savenotes}
	\begin{table}[htb]
		\centering
		% \small
		\pgfplotstabletypeset[
			col sep=comma,
			string type, % Makes the .style={string type} redundant
			columns/Name/.style={string type},
			columns/Type/.style={string type},
			columns/HPC/.style={string type},
			columns/Parallelism/.style={string type},
			columns/Arch./.style={string type},
			columns/Free/.style={string type},
			columns/Source/.style={string type},
			columns/Notes/.style={
				preproc cell content/.style={@cell content=\footnote{##1}}
			},
		]{platforms.csv}
	\end{table}
\end{savenotes}

\bibliographystyle{acm}
\bibliography{drp}
